---
title: "Benchmarking fastpeRmute"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Benchmarking fastpeRmute}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette, we benchmark the performance of `fastpeRmute` against the `gtools` package, which provide similar functionalities. For this, we utilize the `microbenchmark` package to measure execution times for various functions under different scenarios.

```{r setup, include=FALSE}
library(microbenchmark)
library(ggplot2)
library(dplyr)
```

## Combinations with Repetition

```{r}
mb_comb_with_rep <- microbenchmark(
  fastpeRmute = fastpeRmute:::combinationsWithRepetition(20, 5),
  gtools = gtools::combinations(n = 20, r = 5, repeats.allowed = TRUE),
  times = 100L
)

df_comb_with_rep <- as.data.frame(mb_comb_with_rep)

ggplot(df_comb_with_rep, aes(x = expr, y = time)) + 
  geom_boxplot() + 
  theme_minimal() + 
  labs(title = "Combinations with Repetition", y = "Time (nanoseconds)", x = "Function") + 
  coord_flip()
```

## Combinations without Repetition

```{r}
mb_comb_without_rep <- microbenchmark(
  fastpeRmute = fastpeRmute:::combinationsWithoutRepetition(20, 5),
  combn = combn(x = 20, m = 5),
  gtools = gtools::combinations(n = 20, r = 5, repeats.allowed = FALSE),
  times = 100L
)

df_comb_without_rep <- as.data.frame(mb_comb_without_rep)

ggplot(df_comb_without_rep, aes(x = expr, y = time)) + 
  geom_boxplot() + 
  theme_minimal() + 
  labs(title = "Combinations without Repetition", y = "Time (nanoseconds)", x = "Function") + 
  coord_flip()
```

## Permutations without Repetition

```{r}
mb_perm_without_rep <- microbenchmark(
  fastpeRmute = fastpeRmute:::permutationsWithoutRepetition(15,5),
  gtools = gtools::permutations(n = 15, r = 5, repeats.allowed = FALSE),
  times = 100L
)

df_perm_without_rep <- as.data.frame(mb_perm_without_rep)

ggplot(df_perm_without_rep, aes(x = expr, y = time)) + 
  geom_boxplot() + 
  theme_minimal() + 
  labs(title = "Permutations without Repetition", y = "Time (nanoseconds)", x = "Function") + 
  coord_flip()
```

## Permutations with Repetition

```{r}
mb_perm_with_rep <- microbenchmark(
  fastpeRmute = fastpeRmute:::permutationsWithRepetition(15,5),
  gtools = gtools::permutations(n = 15, r = 5, repeats.allowed = TRUE),
  times = 100L
)

df_perm_with_rep <- as.data.frame(mb_perm_with_rep)

ggplot(df_perm_with_rep, aes(x = expr, y = time)) + 
  geom_boxplot() + 
  theme_minimal() + 
  labs(title = "Permutations with Repetition", y = "Time (nanoseconds)", x = "Function") + 
  coord_flip()
```

From the benchmark results, we can see the performance differences between `fastpeRmute`, `gtools`, and base-r functions when they exist.

