---
title: "fastpeRmute"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fastpeRmute}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# fastpeRmute: Fast Combinations and Permutations in R

The fastpeRmute package offers efficient functions for computing combinations and permutations with and without repetition in R. It is tailored for high performance and provides functionality that can be faster than both base R and the gtools package.

## Installation

To install the latest development version from GitHub:
```
devtools::install_github("your_github_username/fastpeRmute")
```

## Examples

### Combinations

#### Without Repetition

Load the library:
```{r}
library(fastpeRmute)
library(tidyverse)
```

Compute combinations without repetition:
```{r}
combinations(n = 10, r = 4)
```

#### With Repetition

Compute combinations with repetition:
```{r}
combinations(n = 10, r = 4, repeats.allowed = T)
```

### Permutations

#### Without Repetition

Compute permutations without repetition:
```{r}
permutations(n = 4, r = 2)
```

#### With Repetition

Compute permutations with repetition:
```{r}
permutations(n = 4, r = 2, repeats.allowed = T)
```

## Performance Benchmark

Let's benchmark the performance of fastpeRmute against base R and gtools:

### Combinations With Repetition

fastpeRmute:
```{r}
system.time(result <- fastpeRmute:::combinationsWithRepetition(60, 5))
```

gtools:
```{r}
system.time(result2 <- gtools::combinations(n = 60, r = 5, repeats.allowed = TRUE))
all((result %>% as_tibble() %>% arrange(V1,V2,V3,V4,V5) %>% as.matrix()) == result2)
```

### Combinations Without Repetition

fastpeRmute:
```{r}
system.time(result <- fastpeRmute:::combinationsWithoutRepetition(60, 5))
```

base R:
```{r}
system.time(combn(x = 60, m = 5))
```

gtools:
```{r}
system.time(result2 <- gtools::combinations(n = 60, r = 5, repeats.allowed = FALSE))
all((result %>% as_tibble() %>% arrange(V1,V2,V3,V4,V5) %>% as.matrix()) == result2)
```

### Permutations Without Repetition

fastpeRmute:
```{r}
system.time(result <- permutations(30,5))
```

gtools:
```{r}
system.time(result2 <- gtools::permutations(n = 30, r = 5, repeats.allowed = FALSE))
all((result %>% as_tibble() %>% arrange(V1,V2,V3,V4,V5) %>% as.matrix()) == result2)
```

### Permutations With Repetition

fastpeRmute:
```{r}
system.time(result <- permutations(50,5, repeats.allowed = TRUE))
```

gtools:
```{r}
system.time(result2 <- gtools::permutations(n = 50, r = 5, repeats.allowed = TRUE))
all((result %>% as_tibble() %>% arrange(V1,V2,V3,V4,V5) %>% as.matrix()) == result2)
```

As observed in the benchmarks, fastpeRmute provides a competitive performance edge, ensuring faster computations for large datasets.

## Contributions & Feedback

Feel free to raise issues, contribute to the codebase, or provide any feedback about the package on our [GitHub repository](https://github.com/your_github_username/fastpeRmute).
